Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-08-16 manuscript.tex
un poco mas de texto

In this section we analyze the distribution of the waiting times for
a first contact.
%
Such distribution can be considered to compute the probability of
reaching a first contact within the first XX years of a SETI project,
assuming the methods are correct and the hypotheses of the experiment.

In the Fig.~\ref{F_waiting} we show the fraction of the CETIs that
have made at least one contact  as a funtion of the elapsed time since
the awakening, given that they make at least one contact on their
lifetime, for different models.
%
From a frequentist approach, the normalizaed cumulative counts are
related to the estimation of the probability of observing a given time
with no success.
%             
XX panels show the histograms of the waiting times for the first
contact, for all the CETIs that make at least one contact along their
lifetime.
%
We show separately the histograms for several values of $\tau_a$ and a
fixed value of $(\tau_s, D_{max})$, and for several values of $\tau_s$ and a
fixed value of $(\tau_a, D_{max})$.
%
For different values of $\tau_a$, the shape of the distribution is
similar, and the main difference given by the different number of
contacts on the different models.
%
Conversely, 
 For different values of $\tau_a$, the shape of the distribution is
similar, and the main difference given by the different number of
contacts on the different models.

@@

@@

@@

\hline
\end{tabular}
\caption{Selected models to analize the behevior of some variables.}
\label{T_SelectedModels}
\end{table*}

@@

@@

\begin{figure*}
   \centering
   \includegraphics[width=0.33\textwidth]{waiting_a_acum_log.png}%
   \includegraphics[width=0.33\textwidth]{waiting_a_acum_lin.png}%
   \includegraphics[width=0.33\textwidth]{waiting_a_dif.png}

   \includegraphics[width=0.33\textwidth]{waiting_s_acum_log.png}%
   \includegraphics[width=0.33\textwidth]{waiting_s_acum_lin.png}%
   \includegraphics[width=0.33\textwidth]{waiting_s_dif.png}

   \caption{Fraction of the CETIs that have made at least one contact  
   as a funtion of the elapsed time since the awakening, given that
   they make at least one contact on their lifetime.
   %
   From a frequentist approach, this fraction is the estimation of the
   probability    
   }
   \label{F_waiting}
\end{figure*}

\begin{figure*}
   \centering
   \includegraphics[width=0.5\textwidth]{Figure_taua.png}%
   \includegraphics[width=0.5\textwidth]{Figure_taus.png}%
   %
   \caption{Histograms of the mean waiting times for the first contact, for
   several models.
   %
   Left panel shows the histograms for several values of $\tau_a$, and
   $\tau_s$ in the range 17000-24000 yr.
   %
   Right panel shows the histograms for several values of $\tau_s$, and
   $\tau_a$ in the range 68000-100000 yr.
   %
   The shape of the histograms does not change when $\tau_a$ is
   modified, but significantly changes when $\tau_s$ is modified.
   }
   \label{F_waiting}
\end{figure*}

\begin{figure*}
   \centering
   \includegraphics[width=0.33\textwidth]{prob1_10k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_40k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_80k.png}
   %
   \caption{F}
   \label{F_waiting}
\end{figure*}

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{radial.png}
   \caption{Fraction of CETIs making cero, one, two or three contacts as a function of
   galactocentric distance.}
   \label{F_res_5}
\end{figure}

\ack[Acknowledgement]{
%
This work was partially supported by the Consejo Nacional de
Investigaciones Cient\'{\i}ficas y T\'ecnicas (CONICET, Argentina),
the Secretar\'{\i}a de Ciencia y Tecnolog\'{\i}a, Universidad Nacional
de C\'ordoba, Argentina, and the Universidad Católica de Córdoba,
Argentina.
%
This research has made use of NASA's Astrophysics Data System.
%
Plots and simulations were made with software developed by the authors
using R and python languajes, plots were postprocessed with inkscape.
%
}

>>>>

In this section we analyze the distribution of the waiting times for
a first contact.
%
Such distribution can be considered to compute the probability for a
random CETI to carry out a SETI project and spend a given time until
the first contact is made.
%
Reaching a first contact within the first $t_1$ years of a SETI project,
requires assuming that the methods are correct and the hypotheses of
the experiment fullfil.
%
This values can be considered as upper limits, since the efficiency of
a SETI initiative could be smaller than the ideal.
%
Also, a civilization could consider itself as "awakened" before it
discovers the right technology to perform a communication.

In the Fig.~\ref{F_waiting} we show the fraction of the CETIs that
have made at least one contact as a funtion of the elapsed time since
the awakening, given that they make at least one contact on their
lifetime, for different models.
%
From a frequentist approach, the normalized cumulative counts are
related to the estimation of the probability of observing a given time
with no success.
%             
Both panels show the histograms of the waiting times for the first
contact, for all the CETIs that make at least one contact along their
lifetime.
%
We show separately the histograms for several values of $\tau_a$ and a
fixed value of $(\tau_s, D_{max})$, and for several values of $\tau_s$ and a
fixed value of $(\tau_a, D_{max})$.
%
For different values of $\tau_a$, the shape of the distribution is
similar, and the main difference given by the different number of
contacts on the different models.
%
Conversely, 
 For different values of $\tau_a$, the shape of the distribution is
similar, and the main difference given by the different number of
contacts on the different models.

@@

%    \caption{Fraction of the CETIs that have made at least one contact  
%   as a funtion of the elapsed time since the awakening, given that they make at least one contact on their lifetime.
%   %
%   From a frequentist approach, this fraction is the estimation of the
%   probability}

@@

On the Figure~\ref{F_radial} we show the fraction of CETIs that make
zero, one, two or three contacts, as a function of the galactocentric
distance.
%
For this model, which corresponds to XXX, the majority of CETIs do not
make any contact during all the time period in which they are active.
%
As expected, the fractions of CETIs making at least one contact
diminishes as the number of contacts rises.
%
The shape of this distribution is a result of the geometry of the GHZ.
%
In general, a closer position to the center of the Galaxy slightly favours 
the posibility of a contact.
%
This would indicate that the position of the Earth is suitable for the
odds of making a contact.

@@

\hline
\end{tabular}
\caption{Selected models to analize the behevior of simulation outputs
   and their dependence on simulation outputs and their dependence on
   simulation parameters..}
\label{T_SelectedModels}
\end{table*}

@@

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{radial.png}
   \caption{Fraction of CETIs making cero, one, two or three contacts as a function of
   galactocentric distance.}
   \label{F_radial}
\end{figure}

@@

\begin{figure*}
   \centering
   \includegraphics[width=0.5\textwidth]{Figure_taua.png}%
   \includegraphics[width=0.5\textwidth]{Figure_taus.png}
   %
   \caption{Histograms of the mean waiting times for the first contact, for
   several models.
   %
   Left panel shows the histograms for several values of $\tau_a$, and
   $\tau_s$ in the range 17000-24000 yr.
   %
   Right panel shows the histograms for several values of $\tau_s$, and
   $\tau_a$ in the range 68000-100000 yr.
   %
   The shape of the histograms does not change when $\tau_a$ is
   modified, but significantly changes when $\tau_s$ is modified.
   }
   \label{F_waiting}
\end{figure*}

\ack[Acknowledgement]{
%
This work was partially supported by the Consejo Nacional de
Investigaciones Cient\'{\i}ficas y T\'ecnicas (CONICET, Argentina),
the Secretar\'{\i}a de Ciencia y Tecnolog\'{\i}a, Universidad Nacional
de C\'ordoba, Argentina, and the Universidad Cat\'olica de C\'ordoba,
Argentina.
%
This research has made use of NASA's Astrophysics Data System.
%
Plots and simulations were made with software developed by the authors
using R and python languajes, plots were postprocessed with inkscape.
%
}
